RNAseq aCRY pCRY data dive

### 2024-04-22 2_A_dive_aCRY_pCRY/2_A_dive_aCRY_pCRY.Rmd
vulcano start

# Macbook
scriptdir <- rstudioapi::getSourceEditorContext()$path
gitdir <- scriptdir %>% dirname() %>% dirname()
dir <- "/Users/simonkelterborn/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/NGS (RNA-Seq & CRISPR)/Chlamy RNA-Seq aCRY"

@@

# 3. Results

>>>>

# Macbook
scriptdir <- rstudioapi::getSourceEditorContext()$path
gitdir <- scriptdir %>% dirname() %>% dirname()

if(Sys.info()["sysname"]== "Linux"){
  s <- "/mnt/s"
  dir <- paste(s,"AG/AG-Scholz-NGS/Daten/Simon/Chlamy_RNASeq_aCRY",sep="/")} else {
    if(Sys.info()["sysname"]== "Darwin"){
       s <- "/mnt/s"
       dir <- "/Users/simonkelterborn/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/NGS (RNA-Seq & CRISPR)/Chlamy RNA-Seq aCRY"} else {
       s <- "S:" 
       dir <- paste(s,"AG/AG-Scholz-NGS/Daten/Simon/Chlamy_RNASeq_aCRY",sep="/")}}

@@

# 3. Results
## Make results
```{r, eval=FALSE, include=FALSE, echo=FALSE}
